### 2012-04-08 trunk/tr-semanticsearchsurvey-data/intro.tex
Changes to intro

\subsection{Many Unsolved Long-tail Queries}
Modern search engines can effectively interpret the topics (semantic themes) and based on that, disambiguates the need intended in the provided query inputs. Combined with additional (query-independent) factors such as PageRank, they are able to address a large fraction of common information needs. In particular, queries that request for pages 
%about a particular topic (\emph{topical query}) or 
representing popular entry points to commonly used information that can be reached via further browsing activities (\emph{navigational queries}), can be successfully processed. These queries work particularly well when the entry points represent named entities (and these named entities are mentioned in the query). For instance, when searching for a concrete product, current search engines are not only able to correctly return matching pages, but also meaningful summaries containing core information about that product. Such a query is rather \emph{unambiguous}, i.e. captures a unique meaning. However, dealing with the large number of queries in the ``long tail'' of Web query logs \cite{} remains challenging. Two particular categories of problematic cases are ambiguous and complex queries:

%\begin{itemize}
%	\item 
	\textbf{Ambiguous Queries:} These queries contain ambiguous terms, resulting in many possible interpretations (several query meanings). For instance, the query ``young scholars from Germany'' is difficult to process because without any additional context, it is not clear who is ``young'', and different types of people may be considered as ``scholars''. Especially difficult are queries, which search for secondary meanings, e.g. ``George Bush'', not the president but the beer brewer.

%	\item 
	\textbf{Complex Queries:} this class of queries captures complex information needs, which may involve several entities and relationships between them. As an example, we have a query that mentions a person and a location, and asks for a relationship between that person and another location (relational queries):  ``birthplace of 32 year old computer scientist, who lives in Karlsruhe, a city in Germany''. 
%\end{itemize}

>>>>

Modern search engines are efficient in retrieving documents (web pages in the case of web search) from large collections based on matching the text of the user's query with the textual content of the document or words in linking to the current document (\emph{anchortext}). These textual features are often combined with additional features that measure the popularity of results based on usage data (\emph{click-behaviour} or using metrics computed on the web graph such as \emph{PageRank} and its derivates. In combination, these relatively simple, but scalable matching techniques are are able to address a large fraction of common information needs. They work particularly well when the user is able to explicitly name the target of the query, this reference is unambiguous and refers to a popular item widely referred to with that name. An example is a product search, where the user enters the name of the product and that product is widely known by that name, e.g \emph{canon ixus 115}, a digital camera.

\subsection{Many Unsolved Long-tail Queries}

While search engines have been effective in addressing common needs, most queries are still in the ``long tail'' of Web query logs. Baeza-Yates et al. report that even in a full year of query logs 88\% of the unique queries are singleton queries, i.e. appeared only once in the year. A lot of this variety comes from syntactic variations of the same popular need and can be addressed with spell-corrections and query suggestion techniques. However, the remaining queries tend to be less common because they refer to less popular needs that need disambiguation or require more complex explanation.

%\begin{itemize}
%	\item 
	\textbf{Ambiguous Queries:} 
	Ambiguous queries arise naturally when the user may not be able to name precisely the item that is sought. Coming back to the example of product search, a user who is in the early stages of selection may not know exactly which product to look for. In this case, the user may name one or two characteristics of the product, such as \emph{cheap digital camera}. The concept of digital camera covers a broad range of actual entities, and there might be some discussion as to which of these can be considered cheap.There are also systemic factors that lead to an increase in ambiguity. Despite the expectation that longer queries should leave to better results, current search engines perform poorer on longer specifications of the same information need, largely because search engines employ an AND semantics between words, and the space of documents that contain all the words becomes smaller with every word added and determining the important words becomes more difficult. Thus users have learned to avoid long queries, leading to shorter but more ambiguous queries. Lastly, users will try to find what they are looking for with the least possible words, adding additional terms after realizing that their original query was ambiguous. For example, when searching for people the user may type in a name, only to realize that there are multiple persons with the same name. Often, this is aggravated by the bias toward a single popular answer. For example, when searching for 'George Bush', the top results are crowded by references to the same person, even though this is a common name. \footnote{For other notable persons named George Bush, see \url{http://en.wikipedia.org/wiki/George_Bush_\%28disambiguation\%29}}.

%	\item 
	\textbf{Complex Queries:} We include in this class all queries that go beyond a reference to a single named entity, and involve several entities and relationships between them. These queries arise again when the user does not know the answer to a question and therefore has to describe the item sought and it's relationships to other items that he or she can name. For example, searching for this paper by the name of the second author is relatively straightforward. However, assuming the user does not know (or do not remember) the name, he or she might look for a "semantic search survey paper written by a researcher at yahoo". Complex queries are particularly hard to address in the traditional information retrieval paradigm when they require information extraction and aggregation, i.e. when not all the entities and relationships are mentioned in a single document. Queries for events naturally involve multiple entities, typically the participant in the event and a reference to another item, e.g. \emph{barrack obama birth certificate}. 
%\end{itemize}
